### 2018-03-29 pkg/mapmisc/inst/extdoc/mapLayers.Rmd
fixing the caching, should solve cran errors
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@1964 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{Examples of map layers}
-->

# Examples of map layers

This document will be incomplete if `rgdal` is unavailable or there is on
internet connection when this document is compiled.  The full document is at
[diseasemapping.r-forge.r-project.org](http://diseasemapping.r-forge.r-project.org).

@@

fact = 0.5
allTiles = FALSE

# uncomment for nicer images
# fact = 1 
# reRun = TRUE
# or run in sandbox	
# R --slave -e "knitr::knit('../pkg/mapmisc/vignettes/mapLayers.Rmd')" fact=1 allTiles=TRUE
# pandoc --to=html5 --output=mapLayers.html mapLayers.md
# cp -r figure ../www
# cp -r mapLayers.html ../www
theArgs = grep("^(fact|allTiles)=", commandArgs(), value=TRUE)
for(D in theArgs)
  eval(parse(text=D))

opts_chunk$set(dpi=50*fact, 
  dev.args=list(bg='white'))

if(allTiles) {
  theNames = names(osmTiles())
  cachePath = file.path(tempdir(), 'mapLayersVignetteCache')
} else {
  # smaller selection of tiles, which are distributed with the package
  theNames = names(grep(
      "cyclemap|thunderforest|waze|wikimedia|korona|opentopomap|maptoolkit|nrcan", 
    osmTiles(), invert=TRUE, value=TRUE))
  cachePath = system.file('extdata', package='mapmisc')
}

@@

  nfTiles = openmap(stjohns, zoom=14, path=theNames,
    verbose=TRUE, 
    crs = crsMerc, 
    cachePath = cachePath)

@@

@@

```{r additionalMichelin, echo=TRUE, purl=FALSE, eval=unlist(mget("allTiles", ifnotfound=FALSE))}

@@

```{r stamenRetina, echo=TRUE, purl=FALSE, eval=unlist(mget("allTiles", ifnotfound=FALSE))}

@@

```{r aditionalEsri, echo=TRUE, purl=FALSE, eval=unlist(mget("allTiles", ifnotfound=FALSE))}

>>>>

```{r theHeader, echo=FALSE, result='asis'}
if(requireNamespace("Pmisc", quietly=TRUE)) {
  Pmisc::markdownHeader(
    title="Examples of map layers in the mapmisc package",    
    author='Patrick Brown'
    )
} else {
cat("# Examples of map layers in the mapmisc package")  
}
```

The full document is at
[diseasemapping.r-forge.r-project.org](http://diseasemapping.r-forge.r-project.org).

@@

fact = 2
allTiles = FALSE

knitr::opts_chunk$set(dpi=150, dev.args=list(bg='white'),
    fig.path = 'mapLayersFigures/', out.width='30%')

theNames = names(osmTiles())
cachePath = file.path(getwd(), 'mapLayersCache')

@@

  nfTiles = openmap(stjohns, zoom=14, path=theNames,
    verbose=TRUE, 
    crs = crsMerc, 
    cachePath = cachePath)
```

@@

Maps shown because it is not clear how they should be attributed.

@@

```{r additionalMichelin, echo=TRUE, purl=FALSE, eval=FALSE}

@@

```{r stamenRetina, echo=TRUE, purl=FALSE, eval=FALSE}

@@

```{r aditionalEsri, echo=TRUE, purl=FALSE, eval=FALSE}
